Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 algorithm_regret.tex
fixing issue in thm 3

In the low-probability event, we simply 
bound the maximum regret by \MAXR.
Now, applying Lemma~\ref{lem:phase-length},
the total expected regret from large-regret steps is at most
$\sum_{s = 1}^T \frac{24 \ARMNUM d}{T^2} \cdot \MAXR \cdot \ARMNUM \log(s)
\leq 12 \ARMNUM^2 d \MAXR.$
%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.  What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \ARMNUM^2 \MAXR d
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}

>>>>

In the low-probability event, we simply 
bound the maximum regret by \MAXR.
\pfedit{Summing over the $T$ time periods,}
\pfdelete{Now, applying Lemma~\ref{lem:phase-length},}
the total expected regret from large-regret steps is at most
$\pfedit{24 \ARMNUM d \MAXR / T.}$
%\pfcomment{I deleted the left-hand side of the above equation because it was using random terms in the summand, and actually wasn't true.  What was intended was an expectation outside of the sum, but I thought it simpler just to delete that term.}

Adding all four types of regret terms,
and substituting 
$\EarlyCut[2]{s} = \frac{128\log(T) \cdot \Diam^2 d^2 \sigma^2}{1.8 s}$,
the cumulative regret up to time $T$ is at most
$
O \left(\ARMNUM \MAXR \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \MAXR \log^2(T)
+ \pfedit{\frac{\ARMNUM \MAXR d}{T}}
+ \ARMNUM \TieDensity \cdot \sum_{s=1}^{T} \EarlyCut[2]{s} \log(s) \right)\\
= 
O \left(\ARMNUM  \cdot \exp \left( \frac{2}{p} \right)
+ \ARMNUM \TieDensity \cdot \log^3(T) \right)$.\QED
\end{emptyextraproof}
